Reproducible Validation and Replication Studies in Nanoscale Physics

### 2020-09-04 tex/results.tex

\paragraph{Mesh:}
For the case with aspect ratio $AR=4$, we have a non-uniform triangular surface mesh ($N=4398$) provided to us by the authors of 
Ellis et al., which we used for validation and replication of Figure 2a of their paper. However, for the replication
of Figure S4 of the supplementary material, we needed the remaining aspect ratio meshes. We generated uniform meshes using our
Python script, and we determined the density of these meshes by comparing the extinction cross section for the case with $AR=4$ of 
our mesh and the one provided by Ellis et al. We noticed that using around double the elements ($N=8564$) than in the original mesh and 
rounding the edges, the relative errors for the extinction cross section were, on average, smaller than 3$\%$, and the variation on the wavelength peak
position was smaller than 1 cm$^{-1}$. This analysis led us to a mesh density of $\approx \; 1.7 \times10^{-5}$ triangles per Angstrom-squared to create the meshes for 
the aspect ratio variation study.

>>>>

\paragraph{Mesh:}
For the case with aspect ratio $AR=4$, we have a non-uniform triangular surface mesh ($N=4398$) provided to us by the authors of 
Ellis et al., which we used for validation and replication of Figure 2a of their paper. However, for the replication
of Figure S4 of the supplementary material, we needed the remaining aspect ratio meshes. We generated uniform meshes using our
Python script, and we determined the density of these meshes by comparing the extinction cross section for the case with $AR=4$ of 
our mesh and the one provided by Ellis et al. We noticed that using around double the elements ($N=8564$) than in the original mesh and 
rounding the edges, the relative errors for the extinction cross section were, on average, smaller than 3$\%$, and the variation on the wavelength peak
position was smaller than 1 cm$^{-1}$. This analysis led us to a mesh density of $\approx \; 1.7 \times10^{-5}$ triangles per $\text{\AA}$ squared to create the meshes for 
the aspect ratio variation study.
